Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-06-24 latex/paper.tex
重新画了一些图，并写了相关文字

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-06-23 15:56:59
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,2}$}
\author{Zhi-Xin Guo${}^{3}$}
\author{Shi-you Chen}
\author{Hongjun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{
${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}
\begin{abstract}
By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
\begin{description}
\item[Keywords]
Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
\end{description}
\end{abstract}

@@

Silicon nano is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment. And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon. The study of multilayer silicon is also helpful to understand the physical evolution of matter from low dimension to high dimension. In addition, the preparation process of silicon nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.

@@

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/pr_total}
\caption{\label{fig:pr_total} (color online) The participation ratio .}
\end{figure}

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/pr_direction}
\caption{\label{fig:pr_direction} (color online) The participation ratio .}
\end{figure}

The total scattering thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table2}. It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure). In addition, the 2lr3 with small top and bottom buckling possesses the most anisotropy, which can reach 57.3\%. The smallest is 2l2 and 2lh (20\%). The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicon. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

@@

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/bands}
\caption{\label{fig:bands}(color online) The phonon dispersion of multilayer silicon along high-symmetry points. (a)2l1 and (b) 2l2 are bilayer structure (c) 3l1 is trilayer structure, (d) 4l1 is four-layer structure and (e) 6l1 width six layers, (f)10l1 with ten layers.}
\end{figure}
In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we use molecular dynamics to measure the phonon spectra of several typical structures. The $10 \times  10  \times  1$ multilayer structure is chosen. The selected high symmetry points are $K(0.5, 0.5, 0.0) , \Gamma(0.0, 0.0, 0.0), X(0.5, 0.0, 0.0),  Y(0.0, 0.5, 0.0)$, Take points along $ K \rightarrow \Gamma \rightarrow X\rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction. According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport. There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction. FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2. The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conducive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy. Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction. Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease. At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length. The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair. With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged. On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number. Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.

@@

The

@@

@@

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-06-24 17:55:39
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,2}$}
\author{Zhi-Xin Guo${}^{3}$}
\author{Shi-you Chen}
\author{Hongjun Xiang}
\author{Xin-Gao Gong${}^{1,2}$}
\email{xggong@fudan.edu.cn}
\affiliation{
${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
${}^2$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China\\
${}^3$Department of Physics, Xiangtan University, Xiangtan 411105, China
}
\begin{abstract}
By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
\begin{description}
\item[Keywords]
Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
\end{description}
\end{abstract}

@@

Silicon  is currently the only one system, from its monolayer to multilayer, and then to the bulk structure, that have been prepared by experiment. And it has rich and typical structure in the dimension of zero dimension, one dimension and three dimensions, which have laid a very good foundation for the study of two-dimensional scale multilayer silicon. The study of multilayer silicon is also helpful to understand the physical evolution of matter from low dimension to high dimension. In addition, the preparation process of silicon nano materials is mature and the raw materials are rich, and It has a broad application prospect in the fields of micro nano electronics, energy, information and other important fields in the future.

@@

The thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table2}. It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure). In addition, the 2lr3 with small top and bottom buckling possesses the most anisotropy, which can reach 57.3\%. The smallest is 2l2 and 2lh (20\%). The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicon. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

@@

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/bands}
\caption{\label{fig:bands}(color online) The phonon dispersion of multilayer silicon along high-symmetry points. (a)2l1 and (b) 2l2 are bilayer structure (c) 3l1 is trilayer structure, (d) 4l1 is four-layer structure and (e) 6l1 width six layers, (f)10l1 with ten layers.}
\end{figure}

In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we calculated the phonon spectra of several typical structures. The $10 \times  10  \times  1$ multilayer structure is chosen. The selected high symmetry points are $\Gamma(0.0, 0.0, 0.0)$, $X(0.5, 0.0, 0.0)$,  $Y(0.0, 0.5, 0.0)$, Take points along $ X \rightarrow \Gamma \rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction. According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport. There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction. FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2. The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conducive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy. Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction. Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease. At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length. The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair. With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged. On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number. Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.

@@

\begin{figure}[b]
\includegraphics[width=0.48\textwidth]{images/pr_direction}
\caption{\label{fig:pr_direction} (color online) The participation ratio.}
\end{figure}

The anisotropy of phonon participation ratio (PR) \cite{Allen1999} has low contribution to anicotropy of thermal conductivity of low layers but have large contribution to that of large layer structures. In previous work we have proven that  phonon participation ratio has obvious correlation with ballisic thermal transpotation in two dimentional materials\cite{Zhou2016}. The participation ratio of all the structures as shown in FIG.\ref{fig:pr_direction}.PR of both Silicene and 2l1 structures are exactly the same , suggesting that every phonon has been participated by all the atoms ,which means there's no localization. The others all present localization but that of 2l2 is isotropic while  PR is larger for armchair of 2l3 than that of zigag which is consist with their thermal conductivity.

The localization means number of transport channels is reduced by some atoms.FIG.\ref{fig:transmission} shows the phonon transmission function along both zigzag and armchair directions. Similar to the situation of participation ratio, transmission of Silicene,2l1 are close. Especially that of 2l2 areexactly the same, which is due to the structure symmetry of it. The anistropy of the transmission are clearly seen in other structure,such as 2l3,3l1,3l2,4l1, where transmissioin of 2l3 is larger in armchair direction than zigzag,while the others has smaller value in armchair. The localization  contributes a lot to ther anisotropy becuase these trends are silimar to their thermal conductivity.

@@

The ballistic contribution of long wave phonons clearly indicate that localization dominant the anitropy of the structures, but more contribution should origin from phonon scattering. Considering three- phonon scattering, the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation. The result is also consist with the trends of thermal conductivity.

@@

The anisotroy of phonon lifetime is due to the anisotropy of anharmonic effect. The Gruneisen parameters which represent the degree of anharmonic effect is also shown in FIG.\ref{fig:gruneisen}.
The larger the anharmonic effect the smaller the scattering lifetime of the phonons.
